The Folly of the Crowd: \\ Market Inefficiencies in Peer to Peer Lending

### 2015-03-30 draft.Rnw
Added to 5.1. Long caption for table 9.

<<init,echo=FALSE,warning=FALSE,results='hide',message=FALSE,cache=FALSE,eval=TRUE>>=
#DONT CACHE SAYS YIHUI
require(dplyr)              ### Used Extensively
require(ggplot2)            ### Used Extensively
require(gridExtra)          ### For facet plots
require(knitr)              ### For chunk control, compilation
require(leaps)              ### For feature selection
require(lubridate)          ### For date grouping, conversions
require(reshape2)           ### For melt() before ggplot
require(scales)             ### For plots
require(texreg)             ### Regression Output using texreg()
require(tidyr)              ### For spread()
require(xtable)             ### Tabular Output using xtable()
options(scipen=999,digits=4,formatR.arrow=TRUE,width=90)
coruse = 'pairwise.complete.obs'
opts_chunk$set(list(fig.path='figure/minimal-', fig.align='center',echo=FALSE, fig.show='hold',tidy=TRUE,fig.height=5,fig.pos='H',warning=FALSE, message=FALSE,results='asis'))
@

@@

\subsection{Background}
Peer-to-peer lending (``P2PL")  is the practice of lending money to borrowers
over the internet, without going through a traditional financial
intermediary.\footcite{p2pwiki} From April 2006 until December 2010, interest
rates were set by lenders\footnote{For the purposes of this essay, lender and
investor are synonyms.}, who competed for the lowest rate in a reverse auction
model.

@@

\section{Excess Returns}
\subsection{Puzzle: Bad Returns in Early Auction regime}
The key inconsistency with EMH found in the early auction regime data is that a simple loan selection strategy can earn excess returns using publicly available information.
This section explains the methodological approach used to create such a strategy, including discussion of cross-validation and avoidance of look-ahead bias, and closes with a discussion of the excess returns earned by the strategy.

Although Figure \ref{fig:ratevscore} shows that investors charge higher rates to riskier borrowers, the high risk, low-reward data pattern of the early auction regime, shown in Figure \ref{fig:roivscore} suggests that this preference for more credit-worthy borrowers is not extreme enough, since the extra interest charged to riskier borrowers does not, in aggregate, make up for the difference in default likelihood. This suggests that the variables given to investors by Prosper could be better used to assess borrower creditworthiness, and select loans with the lower likelihood of default. In this section, I use a regression model (that a naive investor might be able to use to choose loans) to show that a simple model to assess borrower creditworthiness can select loans, out of sample, that earn higher returns than the loans funded by investors. First I carefully discuss the methodology, which sets up the linear regressions that (1) can be tested by the mean ROI of the loans they choose out of sample, and thus will be penalized for overfitting, (2) are trained on data that would not have been available at the time of the decision (3) uses automated feature selection, so that I, with the benefit of hindsight, don't choose which variables will be included.
\subsection{Methodology}

\subsubsection{Cross Validation Procedure}
<<crossValexp, cache=FALSE>>=
cval = data.frame('Sample'= c('Auction-Early.train', 'Auction-Early.test','Auction-Late-.train','Auction-Late.test',
                             'Prosper-rate.train','Prosper-rate.test'),
                 'Loans'= c(nrow(train),nrow(test),nrow(tr2),nrow(te2),nrow(tr3),nrow(te3)),
                 'Start' =  c(min(train$Date),min(test$Date),min(tr2$Date),min(te2$Date),min(tr3$Date),min(te3$Date)),
                 'End' =  c(max(train$Date),max(test$Date),max(tr2$Date),max(te2$Date),max(tr3$Date),max(te3$Date))) %>%
  transform(Days = as.character(as.numeric(difftime(End, Start))), Start = as.character(Start), End=as.character(End))
xtable(cval, label='cval', caption='This table documents number of loans and dates of the 6 samples used for training and testing regression strategies.')
@
The regime discontinuity splits the data into early auction, late auction and Prosper-rate regimes. To test our predictions out of sample, we split each of these thirds in half. For those familiar with cross validation, regressions are trained on the first half of loans originated under each regime, and tested on the second half. Table \ref{cval} describes the size and periods of the six sub samples. For those less familiar with cross validation, I now describe the six sub samples in words.
\begin{enumerate}
\item \Sexpr{nrow(train)} loans originated between April 21, 2006 and  October 2nd, 2007, are used to generate coefficients for the early auction regime regressions.
\item \Sexpr{nrow(test)} loans originated after October 2nd, 2007, but before October 16, 2008, are used to test  the predictions of the early auction regime regressions. \footnote{Between October 10, 2008 and July 20, 2009, no loans are originated, because Prosper is in the SEC-imposed Quiet Period}
\item \Sexpr{nrow(tr2)} loans originated between July 20, 2009 and  April 26, 2010, are used to generate coefficients for the late auction regime regressions. 
\item \Sexpr{nrow(te2)} loans originated after April 26, 2010, but before December 17, 2010, are used to test the predictions of the late auction regime regressions.
\item \Sexpr{nrow(tr3)} loans originated between Dec 20,2010 and April 28,2011  are used to generate coefficients for the Prosper-rate regime regressions.
\item \Sexpr{nrow(te3)} loans originated between April 29,2010 and August 3rd 2011 are used to generate coefficients for the Prosper-rate regime regressions.
\end{enumerate}

@@

fs= inner_join(filter(tab,model=='Benchmark')
                ,filter(tab,model=='Regression')
                ,by='regime')[c('regime','mn.x','sdev.x','mn.y','sdev.y')]
fs2 = inner_join(fs,dr2,by='regime')
colnames(fs2) = c('Regime','BM.mean','BM.sd','LM.mean','LM.sd','BM.default','LM.default')
fs3 = cbind(fs2[1:3],fs2[6],fs2[4:5],fs2[7])
fs3['Excess'] = fs3$LM.mean - fs3$BM.mean
xtable(fs3,label='aggstats',
       caption='The mean return and standard deviation of return of the loans selected by the Linear Model (LM) compared with all loans (BM for benchmark). BM.default and LM.default are the default rates of the relevant selected loans. Excess returns equals LM.mean - BM.mean', digits=3)

if(FALSE){

  fs2  = transform(fs2, ret = LM.mean - BM.mean, sd = LM.sd - BM.sd, def = LM.default - BM.default)
  bmtab = fs2[c('Regime','BM.mean','BM.sd','BM.default')]
  colnames(bmtab) = c('Regime','Mean ROI','St.Dev','Default rate')
  lmtab = fs2[c('Regime','LM.mean','LM.sd','LM.default')]
  colnames(lmtab) = c('Regime','Mean ROI','St.Dev','Default rate')

  diffs = fs2[c('Regime','ret','sd','LM.default')]
  colnames(diffs) = c('Regime','Return','Variance','Default Rate')
}

@@

<<adjTab, cache=FALSE>>=
entry = data.frame(regime='Auction-Early',total.ROI= mean(o1$roi),stringsAsFactors = FALSE)
adj.tab = group_by(decomp,regime) %>% 
  summarise(total.ROI = sum((1 + meanRoi)*num) / sum(num) -1) %>% 
  transform(regime = ifelse(regime=='Auction-Early','Auction-Early.Adj-borrowers',as.character(regime))) %>%
  rbind(entry) %>% arrange(total.ROI)
xtable(adj.tab, caption='The aggregated results of the Rate Adjustment Experiment.', label='adj',digits=4)
@
At each credit score, an upper bound estimated of the fraction of the ROI gap that would be accounted for by adjusted interest rates can be measured as:
\begin{equation}
rate.factor = \frac{mean(adj.roi)-mean(early.roi)}{mean(late.roi)-mean(early.roi)}
\end{equation}
This \emph{rate factor}\footnote{Visually, think of rate factor as if we are walking up the plot from the red line to green line,  what percentage of the way would we make it before we encountered the blue line.} is, by construction, heavily correlated with the difference in interest rates for each regime.   At the lowest included estimated credit score, 649.5, the difference in average interest rate is 9.3\%, and that difference explains 42.1\% of the 19.2\% difference in average ROI. At the higher buckets, the difference in interest rates for borrowers in the 800-820 credit score bucket was 0.3\%, and this difference explained only 3\% (not half) of the 6\% difference in average ROI.
<<rateSimResults, cache=FALSE,eval=FALSE>>=
auc = filter(decomp, regime=='Auction-Early')
adj = filter(decomp, regime=='Auction-Early.Adj-rate')
pr = filter(decomp, regime=='Auction-Late')
cs = inner_join(auc,adj, by='CreditScoreEst') %>% inner_join(pr,by='CreditScoreEst')

cs.tab =  cs %>% mutate(delta.1 = meanRoi.y - meanRoi.x
                        ,delta.2 = meanRoi - meanRoi.y
                        ,delta.3 = meanRoi -meanRoi.x
                        ,rate.factor =delta.1/delta.3
                        ,delta.rate = meanRate - meanRate.x)
@
The aggregated returns of the regimes, as shown in Table \ref{adj}, indicate that if early auction regime borrowers had self enforced the minimum standards Prosper introduced in the second period, investor returns would have improved by at least 2.8\%. If investors had charged these borrowers the rates similar borrowers were charged in the late auction regime, returns might have improved by another 5.75\%.

@@

\section{Conclusion (TODO)}
\begin{enumerate}
\item Restate results.
\item Central planner intervention may be useful when info gathering costs are high.
\item Future research: same experiment with known ROI. Better time controls? Look at consistent errors in mistakes borrowers made.
\end{enumerate}
\newpage
\begin{appendices}
\section{Prosper's Charged-Off vs. Default Terminology}
\footnote{remove this part?}
After the shutdown, Prosper began using the term ``Charged-Off" to mean that a loan is delinquent past 120 days. We observe more defaults than charge-offs before the shutdown, but more charge-offs than defaults after, likely because of the shift in terminology. According to Prosper's website:
\begin{quote}
In general, a debt or account is considered “charged off” when it is unlikely that further payments will be received. Debts are usually charged off after they remain unpaid for a period of time (e.g., 90 to 180 days). Prosper uses the 120 days as the charge off threshold because loans that become over 120 days past due are eligible for sale to a debt buyer, and we have found that there is a steep drop-off in likelihood of further payments after 120 days of delinquency.
\footnote{\url{http://blog.prosper.com/2008/09/16/charge-offs-explained/}}
\end{quote}

\section{Out of Sample Performance by Credit Grade}
<<retTab2,cache=FALSE>>=
vmeans = res %>% group_by(regime,model,grade) %>%  
  summarise(mn = sum((1+meanUL) *length) / sum(length) -1, n=sum(length))

bm = filter(vmeans, model=='Benchmark'); rm = filter(vmeans, model=='Regression')
csdiffs = inner_join(bm,rm, by=c('grade','regime')) %>% transform(delta = mn.y - mn.x)
excess = spread(csdiffs[c('regime','grade','delta')], grade,delta)
excess = cbind(excess[1],excess[3], excess[c(-1,-3)])
xtable(excess,label='excess',
       caption='The excess returns earned by each regression model on loans in each Credit grade'
       , digits=3)
@
<<os.chart3,cache=FALSE,fig.height=8,fig.width=10, fig.cap='The rois of the loans selected by Each strategy by Credit Grade and Regime. Dotted lines indicate means. For example, In the Prosper-rate (2nd) column in the D (5th) row, the green distribution represents the ROIs of all the Grade D loans selected by the Linear Model'>>=
ggplot(res, aes(x=meanUL,fill=model))  + geom_density(alpha=.7) +
  facet_grid(grade ~ regime, scales='free') + 
  theme_bw() +
  geom_vline(data = vmeans, aes(xintercept=mn,color=model)) +
  labs(x='ROI', y='Density', fill='Model',title='Out of Sample Performance')+
  scale_y_continuous()+
  scale_x_continuous(label=percent, limits = c(-.5,NA))
@
\end{appendices}
\printbibliography
\end{document}

>>>>

<<init,echo=FALSE,warning=FALSE,results='hide',message=FALSE,cache=FALSE,eval=TRUE>>=
#DONT CACHE SAYS YIHUI
require(dplyr)              ### Used Extensively
require(ggplot2)            ### Used Extensively
require(gridExtra)          ### For facet plots
require(knitr)              ### For chunk control, compilation
require(leaps)              ### For feature selection
require(lubridate)          ### For date grouping, conversions
require(reshape2)           ### For melt() before ggplotx
require(scales)             ### For plots
require(texreg)             ### Regression Output using texreg()
require(tidyr)              ### For spread()
require(xtable)             ### Tabular Output using xtable()
options(scipen=999,digits=4,formatR.arrow=TRUE,width=90)
coruse = 'pairwise.complete.obs'
opts_chunk$set(list(fig.path='figure/minimal-', fig.align='center',echo=FALSE, fig.show='hold',tidy=TRUE,fig.height=5,fig.pos='H',warning=FALSE, message=FALSE,results='asis'))
@

@@

%if was all time, why would Prosper use same variables to make grades.
%Some of the evidence is inconsistent with time period argument. Can find variables, once Prosper starts using same variables, no more excess returns. Prosper themselves understood this.
\subsection{Background}
Peer-to-peer lending (``P2PL")  is the practice of lending money to borrowers
over the internet, without going through a traditional financial
intermediary.\footcite{p2pwiki} From April 2006 until December 2010, interest
rates were set by lenders\footnote{For the purposes of this essay, lender and
investor are synonyms.}, who competed for the lowest rate in a reverse auction
model.

@@

\section{Excess Returns}
\subsection{Puzzle: Bad Returns in Early Auction regime}

Although Figure \ref{fig:ratevscore} shows that investors charge higher rates to
riskier borrowers, it also shows that early auction regime investors were
insensitive to differences between low-credit borrowers, and, more generally,
less sensitive to credit score than borrowers in subsequent regimes. 
The high risk, low-reward data pattern of the early auction regime, shown in
Figures \ref{fig:roivscore} \ref{defvscore} show that this sensitivity to credit
score was far too low, and does not come close to making up for the difference
in default likelihood. These claims, however, are both vulnerable to the
critique of an unlucky time period. In this section, I present this essay's key
test of market efficiency: can a simple loan selection strategy earn excess
returns using publicly available information?

The answer is simple, but powerful: when investors set interest rates by
auction, in the early auction and late auction regimes, it is possible to earn
excess returns. Once Prosper starts setting rates, my methodology is no longer
able to earn excess returns.

The rest of this section discusses the methods used to create such a strategy,
and the results of the strategy. In the methodology sub-section, I define
publicly available information as 'the information that would have been
available at origination date, the day a given loan was originated,' and discuss
the the principal challenge with complying with this definition: 
\begin{quote}
On origination day, Investors only know which loans have \emph{already}
defaulted. Many loans will end up defaulting later, but to investors, they appear
to be performing well.
\end{quote}

This insight creates four major challenges. First, we must create a variable, for
each loan, that indicates whether the loan had already defaulted on Origination
date, and use that as the dependent variable in a regression, rather than using
the natural defaulted or ROI variables used in section 4. Second, we must fix a
\emph{cut date} at which we use all publicly available information to train a
linear model, and then use this model to select from the pool of loans that have
not been originated.\footnote{This approach also carries the standard
cross-validation benefit, by penalizing overfitting.} Thirdly and most subtly, an investor would not have known
which variables would be useful predictors of future loan performance, only
which variables had been past predictors of loan performance, as such, I do not
choose the independent variables used by the linear model, an automated feature
selection procedure makes this decision. Finally, during some month after the
\emph{cut date} investors did not know whether the listings in the future would
be more profitable than the listings in the present, so the strategy must choose
10\% of the loans offered in a given month in each credit grade, rather than
considering the full pool of loans and picking the best 10\%.\footnote{The
credit grade constraint is to ensure that the models do not use our hindsight
knowledge that certain credit grades performed poorly to improve performance.}

The methodology sub-section which follows, further explores the nature of
these challenges, the implementation of the solutions, and new challenges
created by the solutions, of which there are thankfully few.
The section then continues with In Sample results, which show that the independent
variables chosen by the feature selection protocol are very similar to the
variables Prosper used to make its more informative grading, and that
mispricings were most predictable in the early auction regime. The section
concludes with Out-of-Sample results, which show that such a strategy can earn
excess out-of-sample returns in the early auction and late auction regimes, when
investors set interest rates, but fails to earn excess returns in the
Prosper-rate regime, when Prosper sets interest rates directly.
\subsection{Methodology}
\subsubsection{Cross Validation Procedure}
<<crossValexp, cache=FALSE>>=
cval = data.frame('Sample'= c('Auction-Early.train', 'Auction-Early.test','Auction-Late-.train','Auction-Late.test',
                             'Prosper-rate.train','Prosper-rate.test'),
                 'Loans'= c(nrow(train),nrow(test),nrow(tr2),nrow(te2),nrow(tr3),nrow(te3)),
                 'Start' =  c(min(train$Date),min(test$Date),min(tr2$Date),min(te2$Date),min(tr3$Date),min(te3$Date)),
                 'End' =  c(max(train$Date),max(test$Date),max(tr2$Date),max(te2$Date),max(tr3$Date),max(te3$Date))) %>%
  transform(Days = as.character(as.numeric(difftime(End, Start))), Start = as.character(Start), End=as.character(End))
xtable(cval, label='cval', caption='This table documents number of loans and dates of the 6 samples used for training and testing regression strategies.')
@
The regime discontinuity splits the data into early auction, late auction and Prosper-rate regimes. To test our predictions out of sample, we split each of these thirds in half. For those familiar with cross validation, regressions are trained on the first half of loans originated under each regime, and tested on the second half. Table \ref{cval} describes the size and periods of the six sub samples. For those less familiar with cross validation, I now describe the six sub samples in words.
\begin{enumerate}
\item \Sexpr{nrow(train)} loans originated between April 21, 2006 and  October 2nd, 2007, are used to generate coefficients for the early auction regime regressions.
\item \Sexpr{nrow(test)} loans originated after October 2nd, 2007, but before October 16, 2008, are used to test  the predictions of the early auction regime regressions. \footnote{Between October 10, 2008 and July 20, 2009, no loans are originated, because Prosper is in the SEC-imposed Quiet Period}
\item \Sexpr{nrow(tr2)} loans originated between July 20, 2009 and  April 26, 2010, are used to generate coefficients for the late auction regime regressions. 
\item \Sexpr{nrow(te2)} loans originated after April 26, 2010, but before December 17, 2010, are used to test the predictions of the late auction regime regressions.
\item \Sexpr{nrow(tr3)} loans originated between Dec 20,2010 and April 28,2011  are used to generate coefficients for the Prosper-rate regime regressions.
\item \Sexpr{nrow(te3)} loans originated between April 29,2010 and August 3rd 2011 are used to generate coefficients for the Prosper-rate regime regressions.
\end{enumerate}

@@

fs= inner_join(filter(tab,model=='Benchmark')
                ,filter(tab,model=='Regression')
                ,by='regime')[c('regime','mn.x','sdev.x','mn.y','sdev.y')]
fs2 = inner_join(fs,dr2,by='regime')
colnames(fs2) = c('Regime','BM.mean','BM.sd','LM.mean','LM.sd','BM.default','LM.default')
fs3 = cbind(fs2[1:3],fs2[6],fs2[4:5],fs2[7])
fs3['Excess'] = fs3$LM.mean - fs3$BM.mean
xtable(fs3,label='aggstats',
       caption='This table compares the out of sample performance of the linear model (LM) strategies to the benchmark (BM). As shown in the next figure. The column names are in the format (Strategy).(statistic), where (LM) for linear model and (BM) for benchmark are the two strategies, and mean return of selected loan (mean), standard deviation of monthly returns (sd) and mean default rate of selected loans (default) are the statistics. For example, the LM.mean column shows the average ROI of a loan selected (out of sample, of course) by the linear model in each of the three regimes. The Excess column is calculated as LM.mean - BM.mean, and thus represents the difference in returns between the loans selected by the linear model and the benchmark over each regime. Notice that the Excess returns are positive for the first two regimes, where investors were involved in setting interest rates, and roughly 0 in the most recent regime, where Prosper set rates directly.', digits=3)
@

@@

<<adjTab, cache=FALSE>>=
entry = data.frame(regime='Auction-Early',total.ROI= mean(o1$roi),stringsAsFactors = FALSE)
adj.tab = group_by(decomp,regime) %>% 
  summarise(total.ROI = sum((1 + meanRoi)*num) / sum(num) -1) %>% 
  transform(regime = ifelse(regime=='Auction-Early','Auction-Early.Adj-borrowers',as.character(regime))) %>%
  rbind(entry) %>% arrange(total.ROI)
xtable(adj.tab, caption='The aggregated results of the Rate Adjustment Experiment.', label='adj',digits=4)
@
At each credit score, an upper bound estimated of the fraction of the ROI gap that would be accounted for by adjusted interest rates can be measured as:
\begin{equation}
rate.factor = \frac{mean(adj.roi)-mean(early.roi)}{mean(late.roi)-mean(early.roi)}
\end{equation}
This \emph{rate factor}\footnote{Visually, think of rate factor as if we are walking up the plot from the red line to green line,  what percentage of the way would we make it before we encountered the blue line.} is, by construction, heavily correlated with the difference in interest rates for each regime.   At the lowest included estimated credit score, 649.5, the difference in average interest rate is 9.3\%, and that difference explains 42.1\% of the 19.2\% difference in average ROI. At the higher buckets, the difference in interest rates for borrowers in the 800-820 credit score bucket was 0.3\%, and this difference explained only 3\% (not half) of the 6\% difference in average ROI.

The aggregated returns of the regimes, as shown in Table \ref{adj}, indicate that if early auction regime borrowers had self enforced the minimum standards Prosper introduced in the second period, investor returns would have improved by at least 2.8\%. If investors had charged these borrowers the rates similar borrowers were charged in the late auction regime, returns might have improved by another 5.75\%.

@@

\section{Conclusion (TODO)}
\begin{enumerate}
\item Restate results.
\item Central planner intervention may be useful when info gathering costs are high.
\item Future research: same experiment with known ROI. Better time controls? Look at consistent errors in mistakes borrowers made.
\end{enumerate}
\newpage
%\begin{appendices}
\section{Appendix}
\subsection{Prosper's Charged-Off vs. Default Terminology}
After the shutdown, Prosper began using the term ``Charged-Off" to mean that a loan is delinquent past 120 days. We observe more defaults than charge-offs before the shutdown, but more charge-offs than defaults after, likely because of the shift in terminology. According to Prosper's website:
\begin{quote}
In general, a debt or account is considered “charged off” when it is unlikely that further payments will be received. Debts are usually charged off after they remain unpaid for a period of time (e.g., 90 to 180 days). Prosper uses the 120 days as the charge off threshold because loans that become over 120 days past due are eligible for sale to a debt buyer, and we have found that there is a steep drop-off in likelihood of further payments after 120 days of delinquency.\footcite{chargeoff}
\end{quote}
\subsection{Out of Sample Performance by Credit Grade}
<<retTab2,cache=FALSE>>=
vmeans = res %>% group_by(regime,model,grade) %>%  
  summarise(mn = sum((1+meanUL) *length) / sum(length) -1, n=sum(length))

bm = filter(vmeans, model=='Benchmark'); rm = filter(vmeans, model=='Regression')
csdiffs = inner_join(bm,rm, by=c('grade','regime')) %>% transform(delta = mn.y - mn.x)
excess = spread(csdiffs[c('regime','grade','delta')], grade,delta)
excess = cbind(excess[1],excess[3], excess[c(-1,-3)])
xtable(excess,label='excess',
       caption='The excess returns earned by each regression model on loans in each Credit grade'
       , digits=3)
@
<<os.chart3,cache=FALSE,fig.height=8,fig.width=10, fig.cap='The rois of the loans selected by Each strategy by Credit Grade and Regime. Dotted lines indicate means. For example, In the Prosper-rate (2nd) column in the D (5th) row, the green distribution represents the ROIs of all the Grade D loans selected by the Linear Model'>>=
ggplot(res, aes(x=meanUL,fill=model))  + geom_density(alpha=.7) +
  facet_grid(grade ~ regime, scales='free') + 
  theme_bw() +
  geom_vline(data = vmeans, aes(xintercept=mn,color=model)) +
  labs(x='ROI', y='Density', fill='Model',title='Out of Sample Performance')+
  scale_y_continuous()+
  scale_x_continuous(label=percent, limits = c(-.5,NA))
@
\subsection{Rate Adjustment Results, by Credit Grade}
<<rateSimResults, cache=FALSE,eval=FALSE>>=
auc = filter(decomp, regime=='Auction-Early')
adj = filter(decomp, regime=='Auction-Early.Adj-rate')
prate = filter(decomp, regime=='Auction-Late')
cs = inner_join(auc,adj, by='CreditScoreEst') %>% inner_join(prate,by='CreditScoreEst')

cs.tab =  cs %>% mutate(delta.1 = meanRoi.y - meanRoi.x
                        ,delta.2 = meanRoi - meanRoi.y
                        ,delta.3 = meanRoi -meanRoi.x
                        ,rate.factor =delta.1/delta.3
                        ,delta.rate = meanRate - meanRate.x)
#TO APPENDIX?
@
%\end{appendices}
\printbibliography
\end{document}
